---
title: "Organizational Student Behavior"
author: "Zuhal"
date: "2023-08-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Exploration

## Import Library and Dataset
```{r, include = FALSE}
library(tidyverse)
library(Hmisc)
library(corrplot)
library(GGally)
library(RColorBrewer)
library(ggcorrplot)
```

```{r}
df <- read_csv("Research Questionnaire.csv")
head(df)
```

```{r}
codebook <- read.csv("codebook.csv")
codebook %>% as.list(codebook)
```
P1 = Organizational Climate
P2 = Motivation
P3 = Participation (Student participation in organization's activity)

Rating Scale:
Strongly Agree (5),	Agree (4), Neutral (3),	Disagree (2),	Strongly Disagree (1)

```{r}
table(df$Gender)
table(df$Student_Year)
```


## Checking the Variables Correlation
```{r}
cor_df =round(cor(df[3:29]), 2)
# check the values in matrix form
# cor_df 
cor_df1 <- as.data.frame(cor_df) 
head(cor_df1)
```

```{r}
df_score <- df[3:29]
p_values <- rcorr(as.matrix(df_score))
# Check if you need
# p_values
```

```{r, fig.dim = c(15, 10)}
corrplot(cor_df, method = "circle")
```

## Exploring Variable x1 (Organizational Climate) on x2 (Motivation) and y (Participation)

Make a visualization function to get a better view of each variables correlation
```{r}
corrplot2 <- function(data,
                      method = "pearson",
                      sig.level = 0.05,
                      order = "original",
                      diag = FALSE,
                      type = "upper",
                      tl.srt = 90,
                      number.font = 1,
                      number.cex = 1,
                      mar = c(0, 0, 0, 0)) {
  library(corrplot)
  data_incomplete <- data
  data <- data[complete.cases(data), ]
  mat <- cor(data, method = method)
  cor.mtest <- function(mat, method) {
    mat <- as.matrix(mat)
    n <- ncol(mat)
    p.mat <- matrix(NA, n, n)
    diag(p.mat) <- 0
    for (i in 1:(n - 1)) {
      for (j in (i + 1):n) {
        tmp <- cor.test(mat[, i], mat[, j], method = method)
        p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
      }
    }
    colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
    p.mat
  }
  p.mat <- cor.mtest(data, method = method)
  col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
  corrplot(mat,
    method = "color", col = col(200), number.font = number.font,
    mar = mar, number.cex = number.cex,
    type = type, order = order,
    addCoef.col = "black", # add correlation coefficient
    tl.col = "black", tl.srt = tl.srt, # rotation of text labels
    # combine with significance level
    p.mat = p.mat, sig.level = sig.level, insig = "blank",
    # hide correlation coefficiens on the diagonal
    diag = diag
  )
}
```

```{r}
organizational_climate <- df_score[1:13]
total_score <- df_score[26:27]
organizational_climate <- cbind(organizational_climate, total_score)
```

```{r, fig.dim = c(15, 10)}
# width = 15, height = 10
corrplot2(
    data = organizational_climate,
    method = "pearson",
    sig.level = 0.05,
    order = "original",
    diag = FALSE,
    type = "upper",
    tl.srt = 75
)
```
Note: Corr value >= 0.45

1. Organizational Climate (P1.2, P1.8, P1.9, P1.11, P1.12) to Motivation (P2_Total)

2. Organizational Climate (P1.8, P1.12) to Participation (P3_Total)

## Exploring Variables Indicators or Questions.

```{r}
subset_df <- data.frame()
subset_df <- df[,c("Gender", "Student_Year", "P1.2", "P1.8", "P1.9", 
                   "P1.11", "P1.12", "P2_Total", "P3_Total")]
subset_df$Student_Year <- as.character(subset_df$Student_Year)
head(subset_df)
```
```{r, fig.dim = c(18, 10)}
#create scatterplot matrix
ggpairs(subset_df[3:9])
```

If we focus on the graph, whatever the previous graphs shows that the Indicator P1.12 (one of the organizational climate indicators) has the higher correlation to the P2_Total (Overall Motivation Score) and P3_Total (Overall Participation Score). Thus, I will dive in these indicators.

### Organization Climate on Motivation and Participation 

P1.12 Statement: "I have an alignment of goal with organizational goals."

```{r}
glimpse(subset_df)
```

```{r, fig.dim = c(15, 10)}
ggplot(subset_df, aes(x = P1.12, y = P2_Total)) +
  geom_point(aes(size = 5, color = Student_Year)) + 
  scale_color_brewer(palette="Dark2") +
  labs(
    title = "Goal alignment on Student Motivation in Organizational Activity",
    subtitle = "Color - Student Year",
    caption = "Source: Survey Data",
    x = "Goal Allignment",
    y = "Student Motivation in Organizational Activity"
  ) + 
  theme(
    plot.title = element_text(color = "#0099f9", size = 20, face =  
                              "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 13, face = "bold", hjust = 0.5),
    plot.caption = element_text(face = "italic", hjust = 0)
  )
```

```{r, fig.dim = c(15, 10)}
ggplot(subset_df, aes(x = P1.12, y = P3_Total)) +
  geom_point(aes(size = P3_Total, color = Student_Year)) + 
  scale_color_brewer(palette="Dark2") +
  labs(
    title = "Goal alignment on Student Participation in Organizational Activity",
    subtitle = "Color - Student Year",
    caption = "Source: Survey Data",
    x = "Goal Allignment",
    y = "Student Participation in Organizational Activity"
  ) + 
  theme(
    plot.title = element_text(color = "#0099f9", size = 20, face =  
                              "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 13, face = "bold", hjust = 0.5),
    plot.caption = element_text(face = "italic", hjust = 0)
  )
```


```{r}
p1.12 <- table(subset_df$P1.12)
barplot(p1.12)
```
```{r, fig.dim = c(15, 10)}
ggplot(subset_df, aes(x = P1.12, fill = Gender)) +
  geom_bar() +
  labs(title = "Goal Alignment by Generation Version 1",
       caption = "Source: Survey Data", 
       x = "Goal Alignment") +
  facet_grid(~Student_Year)
```

```{r, fig.dim = c(15, 10)}
ggplot(data = subset_df, aes(x = P1.12,  fill = Gender)) +
  geom_bar(position = position_dodge(preserve = "single")) +
  labs(
    title = "Goal Alignment by Generation Version 2",
    caption = "Source: Survey Data",
    x = "Goal Allignment") + 
  facet_grid(~Student_Year)
```

```{r, fig.dim = c(15, 10)}
ggplot(data = subset_df, aes(x = P1.12,  fill = Student_Year)) +
  geom_bar(position = position_dodge(preserve = "single")) +
  labs(
    title = "Goal Alignment by Gender",
    caption = "Source: Survey Data",
    x = "Goal Allignment") + 
  facet_grid(~Gender)
```

```{r, fig.dim = c(15, 10)}
ggplot(subset_df, aes(x= P2_Total))+ 
  geom_histogram(aes(fill = Student_Year)) +
  labs(
    title = "The Histogram of Motivation by Generation",
    caption = "Source: Survey Data",
    x = "Student Motivation in Organizational Activity") +
  facet_wrap(~P1.12, ncol = 1)
``` 
## Linear Regression

### Linear Regression with Only Selected Variables

```{r}
# Fit the multiple linear regression model on variable y (Participation)
participation_model = lm(formula = P3_Total ~ P1.2 + P1.8 + P1.9 + 
                                P1.11 + P1.12, data = subset_df)
```

```{r}
# Get the model residuals
model_residuals = participation_model$residuals

# Plot the result
hist(model_residuals)
```
The graph looks like a bell curve

```{r}
# Plot the residuals
qqnorm(model_residuals)
# Plot the Q-Q line
qqline(model_residuals)
```
From the plot, we can observe that almost all portions of the residuals lie in a straight line. Then we can assume that the residuals of the model follow a normal distribution.  

Multicollinearity assumption check: 
```{r, fig.dim = c(15, 10)}
# Remove the Customer Value column
reduced_data <- subset_df %>%  select(-c(Gender, Student_Year,
                                            P2_Total, P3_Total))

# Compute correlation at 2 decimal places
corr_matrix = round(cor(reduced_data), 2)

# Compute and show the  result
ggcorrplot(corr_matrix, hc.order = TRUE, type = "lower",
          lab = TRUE)
```
We can notice there is no strong correlations because all of the value is lower than 0.8.

```{r}
summary(participation_model)
```
The model has an adjusted R-square of 0.33 or 33% of the target variance can be explained by this model features.
As we can see, our P1.12 indicators is the only significant variable. 

### Linear Regression With All Variables

```{r}
# Fit the multiple linear regression model on variable y (Participation)
participation_model2 = lm(formula = P3_Total ~ P1.1 + P1.2 + P1.3 + 
                                P1.4 + P1.5 + P1.6 + P1.7 + P1.8 +
                                P1.9 + P1.10 + P1.11 + P1.12,
                                data = df)
```

```{r}
# Get the model residuals
model_residuals2 = participation_model2$residuals

# Plot the result
hist(model_residuals2)
```

```{r}
# Plot the residuals
qqnorm(model_residuals2)
# Plot the Q-Q line
qqline(model_residuals2)
```
```{r, fig.dim = c(15, 10)}
# Remove the Customer Value column
reduced_data2 <- df %>%  select(-c(Gender, Student_Year,
                                   P1_Total, P2_Total, P3_Total))
reduced_data2 <- reduced_data2 %>%  select(-c(14:24))

# Compute correlation at 2 decimal places
corr_matrix = round(cor(reduced_data2), 2)

# Compute and show the  result
ggcorrplot(corr_matrix, hc.order = TRUE, type = "lower",
          lab = TRUE)
```
We can notice there is no strong correlations because all of the value is lower than 0.8.

```{r}
summary(participation_model2)
```
We still have P1.12 significant with additional indicator that is P1.8.
However, our adjusted R-square a bit lower than the previous value 0.32.

There are still a lot of various indicators that can be explored, especially those with codes P2 (Motivation) and P3 (Participation).

# THANK YOU
